Collective behavior of Suspended Janus Particles via an Integral Equation Method

### 2022-05-14 doc/PRF2022/PRF_main.tex
updates

Similar to shear flow simulations, we then place equilibrium states of all boundary conditions \eqref{eq:bcs} in a rotating Taylor-Green Flow with a length scale $l$,
\begin{equation}
\uu_\infty(\xx) = V_0 \left(-\cos(l{\bf e}_x\cdot\xx)\sin(l{\bf e}_y\cdot\xx){\bf e}_x+\sin(l{\bf e}_x\cdot\xx)\cos(l{\bf e}_y\cdot\xx){\bf e}_y\right).
\end{equation}
%
The magnitude of the vortex flow is controlled by the velocity scale $V_0$.
Similar to the setup in the shear flow cases, we shift the center of mass position to the origin then turn on the Taylor-Green flow with $V_0=0.1$ and tune the sides of zero-velocity box to $\pi$, i.e., $l=0.5$, Figure~\ref{fig:TG_1}(a)--(c) show three frames of simulation results and we 
track the aspect ratio $\lambda$ described in the previous section which is provided in panel (d). 
The stiffness of the multi-lamellar structure is able to compete with the flow therefore the structure
does not deform to any states other than multi-lamellar shape. 
%We also found that the flow strength coefficient above $V_0=0.1$ will result to clear group separations during the simulations.

@@

>>>>

Similar to shear flow simulations, we then place equilibrium states of all boundary conditions \eqref{eq:bcs} in a rotating Taylor-Green Flow with a length scale $l$,
\begin{equation}
\uu_\infty(\xx) = V_0 \left(-\cos(l{\bf e}_x\cdot\xx)\sin(l{\bf e}_y\cdot\xx){\bf e}_x+\sin(l{\bf e}_x\cdot\xx)\cos(l{\bf e}_y\cdot\xx){\bf e}_y\right).
\end{equation}
%
The magnitude of the vortex flow is controlled by the velocity scale $V_0$.
Similar to the setup in the shear flow cases, we shift the center of mass position to the origin then turn on the Taylor-Green flow with $V_0=0.1$ and tune the sides of zero-velocity box to $\pi$, i.e., $l=0.5$, Figure~\ref{fig:TG_1}(a)--(c) show three frames of simulation results and we 
track the aspect ratio $\lambda$ described in the previous section which is provided in panel (d). 
The stiffness of the multi-lamellar structure is able to compete with the flow therefore the structure
does not deform to any states other than multi-lamellar shape. 
We also found that the flow strength coefficient above $V_0=0.1$ will result to clear group separations during the simulations. 
Comparing with the case when $V_0=0.2$, we provide a frame in Figure~\ref{fig:TG_2}(a) and the energy comparison is shown in panel (b). Numerical results validate the phenomenon that a higher taylor green vortex flow generates large structure separations with higher total energy.

@@

\begin{figure}
  \begin{center}
  \includegraphics[width=0.4\textwidth]{TG0p2_2000.png}
  \includegraphics[width=0.4\textwidth]{TG_energy1.jpg}
  \end{center}
  \vspace{-20pt}  
  \caption{\label{fig:TG_2} (a) Snapshots of simulation using boundary condition \eqref{eq:bcs}(b) in a Taylor-Green flow when $V_0=0.2$, $l=0.5$, and $t = 400$. (b) Energy profiles for two cases $V_0=0.1$ and $V_0=0.2$. }
\end{figure}
